Supplementary Information: Quantifying the pathways to life using assembly spaces

### 2021-05-19 papers/assembly/I/main.tex
Flesh out the definition of the basis

\newcommand{\upset}[1]{#1\!\!\uparrow}
\newcommand{\downset}[1]{#1\!\!\downarrow}
\newcommand{\N}{\mathbb{N}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\Min}[1]{\min{(#1)}}
\newcommand{\Max}[1]{\max{(#1)}}
\newcommand{\Minim}{\mathcal{Min}}
\newcommand{\Maxim}{\mathcal{Max}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\powerset}{\mathcal{P}}
\newcommand{\pathway}[1]{\langle~#1~\rangle}

@@

    \smallskip
    Let $X$ be a subset of sites in $P$. We say that $\gamma$ is \textit{from $X$} if $\pi(\sigma(t_1)) \subseteq X$.

    \smallskip
    Let $y$ be site, and let $Y$ be a subset of sites.
    We say $\gamma$ is a \textit{to $y$} if $y \in \pi(\tau(t_n))$, and \textit{to $Y$} if $Y \subseteq \pi(\tau(t_n))$.

@@

\begin{lemma}\label{lem:image-of-pathways}
    Let $f: P \rightarrow Q$ be a Petri net morphism and let $X, Y \subseteq S(P)$ be pathway connected in $P$.
    Then either $f(x)$ and $f(y)$ are pathway connected in $f(P)$.
\end{lemma}
\begin{proof}
    \TODO{Complete}
\end{proof}

\begin{definition}\label{def:site-completion}
    \TODO{Complete}
\end{definition}

\begin{definition}\label{def:generator}
    \TODO{A set of sites from which there is a pathway to every other object}
\end{definition}

\begin{definition}\label{def:basis}
    Let $P$ be a Petri net and $X \subseteq S(P)$.
    We say that $X$ is a basis of $P$ if $\ldots$.
    \TODO{Complete}
\end{definition}

>>>>

\newcommand{\upset}[1]{#1\!\!\uparrow}
\newcommand{\downset}[1]{#1\!\!\downarrow}
\newcommand{\N}{\mathbb{N}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\Min}[1]{\min{(#1)}}
\newcommand{\Max}[1]{\max{(#1)}}
\newcommand{\Minim}{\mathcal{Min}}
\newcommand{\Maxim}{\mathcal{Max}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\powerset}{\mathcal{P}}
\newcommand{\pathway}[1]{\langle#1\rangle}

@@

    \smallskip
    Let $X$ be a subset of sites in $P$. We say that $\gamma$ is \textit{from $X$} if $\pi(\sigma(t_1)) \subseteq X$, an will sometimes say that $\gamma$ starts at $X$.

    \smallskip
    Let $y$ be site, and let $Y$ be a subset of sites.
    We say $\gamma$ is a \textit{to $y$} if $y \in \pi(\tau(t_n))$, and \textit{to $Y$} if $Y \subseteq \pi(\tau(t_n))$, and will sometimes say that $\gamma$ terminates at $y$ or $Y$.

@@

\begin{lemma}\label{lem:image-of-pathways}
    Let $f: P \rightarrow Q$ be a Petri net morphism and let $X, Y \subseteq S(P)$ be pathway connected in $P$.
    Then either $f(X)$ and $f(Y)$ are pathway connected in $f(P)$.
\end{lemma}
\begin{proof}
    \TODO{Complete}
\end{proof}

\begin{definition}\label{def:minimal-maximal}
    Let $P$ be a Petri net and let $x$ be a site in $P$.
    We say that $x$ is minimal in $P$ if the only pathway terminating at $x$ is the zero pathway.
    Similarly, $x$ is maximal in $P$ if the only pathway starting at $x$ is the zero pathway.
    The set of all minimal sites in $P$ is denoted $\Min{P}$, and the set of all maximal sites is denoted $\Max{P}$.
\end{definition}

\begin{definition}\label{def:site-completion}
    \TODO{Given a set of transitions, construct the set of all sites and add all the edges.}
\end{definition}

\begin{definition}\label{def:generator}
    Let $P$ be a Petri net and let $X$ be a subset of sites of $P$.
    We say that $X$ is a \textbf{generating set} of $P$ if $X$ is pathway connected to every subset of sites $Y$ in $P$.
\end{definition}

\red{The set of all generating sets of a Petri net can be ordered by set inclusion}

\begin{definition}\label{def:basis}
    Let $P$ be a Petri net and let $X$ be a set of generators of $P$.
    We say that $X$ is a \textbf{basis} of $P$ if it is minimal in the partially ordered set of generating sets.
    That is, $X$ is a basis if for any other generating set $Y$ of $P$, if $Y \subseteq X$ then $X = Y$.
\end{definition}
